---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wordpiece

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of wordpiece is to allow for easy text tokenization using a wordpiece vocabulary.

## Installation

You can install the released version of wordpiece from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("wordpiece")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("macmillancontentscience/wordpiece")
```

# Examples

This package can be used to tokenize text for modeling.
A common usecase would be to tokenize all text in a data.frame or other tibble.

```{r tokenize_df}
library(wordpiece)
library(dplyr, warn.conflicts = FALSE)
df_tokenized <- tibble(
  text = c(
    "I like tacos.",
    "I like apples with cheese.",
    "The unaffable coder wrote incorrect examples."
  )
) %>% 
  mutate(
    tokens = wordpiece_tokenize(text)
  )

df_tokenized

df_tokenized$tokens[[1]]
```

## Code of Conduct
  
Please note that the wordpiece project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.

## Disclaimer

This is not an officially supported Macmillan Learning product.

## Contact information

Questions or comments should be directed to Jonathan Bratt (jonathan.bratt@macmillan.com) and Jon Harmon (jonthegeek@gmail.com).
